Reproducible methods for modeling combined public transport and cycling trips and associated benefits: \ evidence from the biclaR tool

### 2024-05-08 paper/PaperCEUS/PaperCEUS_rev1.Rmd
doi and urls bib

Combining public transportation (PT) and cycling for the first and last mile in metropolitan areas can replace a high proportion of private car trips [@MARTENS2007326; @van2021insights].
In The Netherlands, which has the highest mode share of cycling in the world, cycling accounts for more than a third of all trips to and from rail stations at the 'home' end of the journey, greatly increasing the ability of the transport system [@RIETVELD200071].
This approach to reducing car dependency and associated externalities requires interventions and programs to make bicycling more appealing [@lapaix_role_2021].
The resulting public investments can have significant social and environmental benefits [@internationaltransportforum_integrating_2017].
Despite the benefits of cycling-PT intermodality, the potential of this combination is often overlooked in transport planning [@lapaix_role_2021].
<!-- Many studies refer to the potential of cycling and bike-sharing to replace car and PT trips, but not to the potential of serving as first and last miles. -->

>>>>

Combining public transportation (PT) and cycling for the first and last mile in metropolitan areas can replace a high proportion of private car trips [@MARTENS2007326; @vanmil_insights_2021].
In The Netherlands, which has the highest mode share of cycling in the world, cycling accounts for more than a third of all trips to and from rail stations at the 'home' end of the journey, greatly increasing the ability of the transport system [@RIETVELD200071].
This approach to reducing car dependency and associated externalities requires interventions and programs to make bicycling more appealing [@lapaix_role_2021].
The resulting public investments can have significant social and environmental benefits [@internationaltransportforum_integrating_2017].
Despite the benefits of cycling-PT intermodality, the potential of this combination is often overlooked in transport planning [@lapaix_role_2021].
<!-- Many studies refer to the potential of cycling and bike-sharing to replace car and PT trips, but not to the potential of serving as first and last miles. -->
